Aa Language Reference Manual

### 2013-09-03 v2/Ahir-asm/devel/docs/AaLRM.tex
Added a comment to highlight the early variable feedback issue in the pipelining of loops.

Note that it is always possible to describe
a do-while loop using a branch-block, and this is what should be done
if loop-pipelining is not desired.

>>>>

Note that it is always possible to describe
a do-while loop using a branch-block, and this is what should be done
if loop-pipelining is not desired\footnote{There are still some issues
with loop-pipelining which are still being sorted out.}.

\subsubsection{Issues with loop-pipelining (in progress)}

There is one outstanding issue: loop run-away.  This issue arises
when an early value is fed back into the loop body which uses delayed
versions of this early value.  The loop races ahead, priming the
delayed versions with junk.  The solution is to always feed back the
most delayed version of a variable.
